\toolname: Property-Based Testing for MPC Security

### 2023-11-03 paper/main.tex
describe decision trees

Chalupka et al. use decision trees (D-Trees) as their ML classifiers.
Because the process requires training many copies of the model, a light-weight model like a D-Tree is preferable;
we also use D-Trees for \toolname.

@@

To actually test a protocol, \toolname uses two identical machine learning (ML) tools to predict the honest secrets based on the corrupt views.
One of the two models has access to the real-world views, and the only has access to the ideal-world views.
In principal, \textit{any} ML classifier is ok to use; the choice is partly an engineering question
and partly a judgment call about what kinds of systems will be best able to discern patterns in the views of the subject protocol.
Generating the data for these tests requires running the protocol many times.
The process is enumerated in Algorithm 1.
Note that the data must be understood as vectors/matrices/tensors of bits;
aggregating values into larger structures such as bytes or integers would at best require careful modifications to line 8 in Algorithm 1.

>>>>

Chalupka et al. use decision trees (D-Trees) as their ML classifiers.
Because the process requires training many copies of the model, a light-weight model like a D-Tree is preferable;
we also use D-Trees for \toolname.
In principal, \textit{any} ML classifier would be ok to use; the choice is partly an engineering question
and partly a judgment call about what kinds of systems will be best able to discern patterns in the views of the subject protocol.

@@

To actually test a protocol, \toolname uses two identical machine learning (ML) tools to predict the honest secrets based on the corrupt views.
One of the two models has access to the real-world views, and the other only has access to the ideal-world views.
Generating the data for these tests requires running the protocol many times.
The process is enumerated in Algorithm 1.
Note that the data must be understood as vectors/matrices/tensors of bits;
aggregating values into larger structures such as bytes or integers would at best require careful modifications to line 8 in Algorithm 1.
